---
title: "Age Histograms"
output: html_notebook
---

```{r}
library(ggplot2)
library(dplyr)
library(stringr)
library(splitstackshape)
library(cowplot)
library(ggpubr)
```


This notebook is used to produce age histogram plots.

```{r}
pillar_2 = read.csv("Data/TTI_Pillar2/AgeDistributionBinnedOriginP2.csv")
sgss = read.csv("Data/TTI_SGSS/AgeDistributionBinnedOriginSGSS.csv")
CSS = read.csv('Data/CovidSymptomStudy/Age.csv')
CIS = read.csv("Data/CommunityInfectionSurvey/AgeDistributionBinned.csv")
```

## CSS reports decades only, compute bin

```{r}
CSS = CSS %>%
  mutate(binRange_1 = Decade*10) %>%
  mutate(binRange_2 = (Decade+1)*10)
```

## CIS reports most of the data for a single year, convert to same format as other datasets

```{r}
CIS = CIS %>% 
  mutate(decade = floor(subset.age_85 / 10)) %>%
  group_by(decade) %>%
  summarise(count = sum(unity))%>%
  mutate(binRange_1 = decade*10) %>%
  mutate(binRange_2 = (decade+1)*10)
```

Manually edit the right interval of the largest bin, since it contains many values.

```{r}
CIS[9,]$binRange_2 = 95
```


## Normlising to ge the density

```{r}
pillar_2 = pillar_2 %>%
  mutate(density = count / sum(count))

sgss = sgss %>%
  mutate(density = count / sum(count))

CSS = CSS %>%
  mutate(density = Count / sum(Count))

CIS = CIS %>%
  mutate(density = count / sum(count))
```

Use regex to split the bins into lower and upper values for the Test & Trace datasets

```{r}
pillar_2$binRange <- str_extract(pillar_2$age_band, "[0-9].*[0-9]+")
pillar_2 <- cSplit(pillar_2, "binRange")

sgss$binRange <- str_extract(sgss$age_band, "[0-9].*[0-9]+")
sgss <- cSplit(sgss, "binRange")
```

```{r}
pillar_2 = pillar_2 %>%
  mutate(binRange_1 = binRange_1 + 1) %>%
  mutate(binRange_2 = binRange_2 + 1)

pillar_2[1]$binRange_1 = 0
pillar_2[10]$binRange_2 = 120
```

```{r}
sgss = sgss %>%
  mutate(binRange_2 = binRange_2 + 1) %>%
  mutate(binRange_1 = binRange_1 + 1)

sgss[1]$binRange_1 = 0
sgss[10]$binRange_2 = 120
```


Compute the bin widths

```{r}
pillar_2 = pillar_2 %>%
  mutate(width = binRange_2 - binRange_1)

sgss = sgss %>%
  mutate(width = binRange_2 - binRange_1)

CSS = CSS %>%
  mutate(width = binRange_2 - binRange_1)

CIS = CIS %>%
  mutate(width = binRange_2 - binRange_1)
```

# create some custom ggplot settings

```{r}
x_scale = scale_x_continuous(
  "Age (years)", 
  seq(from = 0, to = 120, by = 20),
  limits = c(0, 120))

age_histogram = geom_bar(
  stat = "identity"
  #, alpha = 0.6
  , position = "identity"
  ,show.legend = FALSE)

y_scale = scale_y_continuous(
  "Density",
  seq(from = 0, to = 0.3, by = 0.05), limits = c(0, 0.3))
```


```{r}
pillar_2_hist = ggplot(pillar_2,
       aes(
         x = binRange_1 + width/2,
         fill = binRange_1 + width/2,
         y = density,
         width = width
      )) +
  age_histogram + 
  x_scale + 
  y_scale + 
  theme_minimal_grid() +
  ggtitle("a") +
  scale_fill_continuous()


pillar_2_hist
```

```{r}
sgss_hist = ggplot(sgss,
       aes(
         x = binRange_1 + width/2,
         y = density,
         fill = binRange_1 + width/2,
         width = width
      )) +
  age_histogram +
  theme_minimal_grid() +
  x_scale + 
  y_scale + 
  ggtitle("b")

sgss_hist
```

```{r}
CSS_hist = ggplot(CSS,
       aes(
         x = binRange_1 + width/2,
         y = density,
         fill = binRange_1 + width/2,
         width = width
      )) +
  age_histogram +
  theme_minimal_grid() +
  x_scale +
  y_scale +
  ggtitle("c")

CSS_hist
```

```{r}
CIS_hist = ggplot(CIS,
       aes(
         x = binRange_1 + width/2,
         y = density,
         fill = binRange_1 + width/2,
         width = width
      )) +
  age_histogram +
  theme_minimal_grid() +
  x_scale +
  y_scale +
  ggtitle("d")

CIS_hist
```

## Arranging the plots

```{r}
arranged = ggarrange(
  pillar_2_hist,
  sgss_hist,
  CSS_hist,
  CIS_hist,
  ncol = 4,
  nrow = 1,
  show.legend = FALSE)
arranged
```

```{r}
arranged$`1`
```


```{r}
ggsave('Figures/DescriptiveStatistics/Age Distributions.png', arranged$`1`, width = 14, height = 4)
```



