---
title: "UMAP Visualisation"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r}
source('Visualisation/my_functions.R')
```

# Libraries

```{r}
library(ggplot2)
library(ggrepel)
library(dplyr)
library(cowplot)
library(RColorBrewer)
library(gridExtra)
library(ggpubr)
```

# Load and clean data

```{r}
SymptomNameCategoryLookup = read.csv('Data/Lookups/SymptomNameCategoryLookup.csv')
categories = read.csv('Data/Lookups/CategoriesLookup.csv')
```

# Pillar 2

Load in the data and perform some basic data wrangling and joins to lookup tables.

```{r}
p2_children = read.csv("Data/Alignments/AlignedUMAP/Pillar2/children_loose.csv")
p2_adult = read.csv("Data/Alignments/AlignedUMAP/Pillar2/adult_loose.csv")
p2_elder = read.csv("Data/Alignments/AlignedUMAP/Pillar2/elder_loose.csv")

p2_children_symptom_info = read.csv(
  'Data/TTI_Pillar2_AgeStratified/Symptom_infoOriginP2Below18.csv')
p2_adult_symptom_info = read.csv(
  'Data/TTI_Pillar2_AgeStratified/Symptom_infoOriginP218-54.csv')
p2_elder_symptom_info = read.csv(
  'Data/TTI_Pillar2_AgeStratified/Symptom_infoOriginP255Plus.csv')

# rename, makes joins easier
colnames(p2_children_symptom_info)[1] = 'symptom_name_raw'
colnames(p2_adult_symptom_info)[1] = 'symptom_name_raw'
colnames(p2_elder_symptom_info)[1] = 'symptom_name_raw'

p2_children = p2_children %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(p2_children_symptom_info)
p2_adult = p2_adult %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(p2_adult_symptom_info)
p2_elder = p2_elder %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(p2_elder_symptom_info)
```

```{r}
sgss_children = read.csv("Data/Alignments/AlignedUMAP/SGSS/children_loose.csv")
sgss_adult = read.csv("Data/Alignments/AlignedUMAP/SGSS/adult_loose.csv")
sgss_elder = read.csv("Data/Alignments/AlignedUMAP/SGSS/elder_loose.csv")

sgss_children_symptom_info = read.csv(
  'Data/TTI_SGSS_AgeStratified/Symptom_infoOriginSGSSBelow18.csv')
sgss_adult_symptom_info = read.csv(
  'Data/TTI_SGSS_AgeStratified/Symptom_infoOriginSGSS18-54.csv')
sgss_elder_symptom_info = read.csv(
  'Data/TTI_SGSS_AgeStratified/Symptom_infoOriginSGSS55Plus.csv')

# rename, makes joins easier
colnames(sgss_children_symptom_info)[1] = 'symptom_name_raw'
colnames(sgss_adult_symptom_info)[1] = 'symptom_name_raw'
colnames(sgss_elder_symptom_info)[1] = 'symptom_name_raw'

sgss_children = sgss_children %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(sgss_children_symptom_info)
sgss_adult = sgss_adult %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(sgss_adult_symptom_info)
sgss_elder = sgss_elder %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(sgss_elder_symptom_info)
```

```{r}
cis_children = read.csv("Data/Alignments/AlignedUMAP/CIS/children_loose.csv")
cis_adult = read.csv("Data/Alignments/AlignedUMAP/CIS/adult_loose.csv")
cis_elder = read.csv("Data/Alignments/AlignedUMAP/CIS/elder_loose.csv")

cis_children_symptom_info = read.csv(
  'Data/CommunityInfectionSurveyAgeStratified/symptoms_info_18.csv')
cis_adult_symptom_info = read.csv(
  'Data/CommunityInfectionSurveyAgeStratified/symptoms_info_18_54.csv')
cis_elder_symptom_info = read.csv(
  'Data/CommunityInfectionSurveyAgeStratified/symptoms_info_55.csv')

# rename, makes joins easier
colnames(cis_children_symptom_info)[2] = 'symptom_name_raw'
colnames(cis_adult_symptom_info)[2] = 'symptom_name_raw'
colnames(cis_elder_symptom_info)[2] = 'symptom_name_raw'

cis_children = cis_children %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'ONS')) %>%
  inner_join(cis_children_symptom_info, by = c('symptom_name_raw'))
cis_adult = cis_adult %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'ONS')) %>%
  inner_join(cis_adult_symptom_info, by = c('symptom_name_raw'))
cis_elder = cis_elder %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'ONS')) %>%
  inner_join(cis_elder_symptom_info, by = c('symptom_name_raw'))

# multiply by 100 to make consistent with other datasets
cis_children$proportion_of_cases_with_symptom = cis_children$proportion_frompositives / 100
cis_adult$proportion_of_cases_with_symptom = cis_adult$proportion_frompositives / 100
cis_elder$proportion_of_cases_with_symptom = cis_elder$proportion_frompositives / 100
```

```{r}
css_children = read.csv("Data/Alignments/AlignedUMAP/CSS/children_loose.csv")
css_adult = read.csv("Data/Alignments/AlignedUMAP/CSS/adult_loose.csv")
css_elder = read.csv("Data/Alignments/AlignedUMAP/CSS/elder_loose.csv")

css_children_symptom_info = read.csv(
  'Data/CovidSymptomStudyAgeSeperated/DemographicSymptom_children.csv')
css_adult_symptom_info = read.csv(
  'Data/CovidSymptomStudyAgeSeperated/DemographicSymptom_adults.csv')
css_elder_symptom_info = read.csv(
  'Data/CovidSymptomStudyAgeSeperated/DemographicSymptom_elder.csv')

colnames(css_children_symptom_info)[2] = 'symptom_name_raw'
colnames(css_adult_symptom_info)[2] = 'symptom_name_raw'
colnames(css_elder_symptom_info)[2] = 'symptom_name_raw'

css_children = css_children %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'Zoe')) %>%
  inner_join(css_children_symptom_info, by = c('symptom_name_raw'))
css_adult = css_adult %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'Zoe')) %>%
  inner_join(css_adult_symptom_info, by = c('symptom_name_raw'))
css_elder = css_elder %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'Zoe')) %>%
  inner_join(css_elder_symptom_info, by = c('symptom_name_raw'))

css_children$proportion_of_cases_with_symptom = css_children$proportion
css_adult$proportion_of_cases_with_symptom = css_adult$proportion
css_elder$proportion_of_cases_with_symptom = css_elder$proportion
```

Create some ggplot objects that can be shared across the plots.

```{r}
scaling_factor = 100
bubble_plot = geom_point(aes(size = scaling_factor * proportion_of_cases_with_symptom))
bubble_plot_zoe = geom_point(aes(size = scaling_factor * proportion))

symptom_labels = labs(
    size = 'Proportion of cases\nwith symptom (%)',
    color = 'Symptom category'
    )

category_legend = guides(colour = guide_legend(override.aes = list(size=5)))

size_scaling =  scale_size_continuous(
    breaks = c(0, 20, 40, 60, 80, 100),
    labels = c(0, 20, 40, 60, 80, 100),
    limits = c(0, 100),
    range = c(2,6)
   )
```


# Plot Data

This function takes several input datasets, and returns axes that will work for all the datasets

```{r}
compute_ideal_axes = function(dataset_children, dataset_adult, dataset_elder){
  # computing axes to share across the embedding plots

  x_max = max(c(dataset_children$X0, dataset_adult$X0, dataset_elder$X0))
  x_min = min(c(dataset_children$X0, dataset_adult$X0, dataset_elder$X0))
  y_max = max(c(dataset_children$X1, dataset_adult$X1, dataset_elder$X1))
  y_min = min(c(dataset_children$X1, dataset_adult$X1, dataset_elder$X1))
  
  x_center = (x_max + x_min) / 2
  y_center = (y_max + y_min) / 2
  
  x_len = x_max - x_min
  y_len = y_max - y_min
  
  len = max(x_len, y_len)
  
  coord_equal(
    ratio = 1, 
    xlim = c(x_center - len / 2, x_center + len / 2), 
    ylim = c(y_center - len / 2, y_center + len / 2))
}
```

Compute axes for all datasets

```{r}
pillar_2_axes = compute_ideal_axes(
  dataset_children = p2_children,
  dataset_adult = p2_adult,
  dataset_elder = p2_elder)

sgss_axes = compute_ideal_axes(
  dataset_children = sgss_children,
  dataset_adult = sgss_adult,
  dataset_elder = sgss_elder)

cis_axes = compute_ideal_axes(
  dataset_children = cis_children,
  dataset_adult = cis_adult,
  dataset_elder = cis_elder)

css_axes = compute_ideal_axes(
  dataset_children = css_children,
  dataset_adult = css_adult,
  dataset_elder = css_elder)
```


```{r}
# plotting function
create_bubble_plot = function(dataset, title, shared_axes){
  ggplot(
    dataset,
    aes(
      x=X0,
      y=X1,
      label=symptom_name_formatted,
      color = category)) +
    bubble_plot +
    labs(
      title = title) +
    geom_text_repel(
      inherit.aes = FALSE,
      aes(x=X0, y=X1, label = symptom_name_formatted),
      size = 2.5,
      point.padding = 0.5,
      max.overlaps = 20) +
    theme_cowplot() +
    symptom_labels +
    size_scaling + 
    colour_scale_all +
    shared_axes + 
    theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
    grids() + 
    category_legend +
    theme(legend.position="right")
}
```

# create pillar 2 plots

```{r}
p2_children_plot = create_bubble_plot(p2_children, title = 'a', shared_axes = pillar_2_axes)
p2_children_plot
```

```{r}
p2_adult_plot = create_bubble_plot(p2_adult, title = 'b', shared_axes = pillar_2_axes)
p2_adult_plot
```


```{r}
p2_elder_plot = create_bubble_plot(p2_elder, title = 'c', shared_axes = pillar_2_axes)
p2_elder_plot
```

# create sgss plots

```{r}
sgss_children_plot = create_bubble_plot(sgss_children, title = 'a', shared_axes = sgss_axes)
sgss_children_plot
```

```{r}
sgss_adult_plot = create_bubble_plot(sgss_adult, title = 'b', shared_axes = sgss_axes)
sgss_adult_plot
```

```{r}
sgss_elder_plot = create_bubble_plot(sgss_elder, title = 'c', shared_axes = sgss_axes)
sgss_elder_plot
```

## CIS

```{r}
cis_children_plot = create_bubble_plot(cis_children, title = 'a', shared_axes = cis_axes)
cis_children_plot
```

```{r}
cis_adult_plot = create_bubble_plot(cis_adult, title = 'b', shared_axes = cis_axes)
cis_adult_plot
```

```{r}
cis_elder_plot = create_bubble_plot(cis_elder, title = 'c', shared_axes = cis_axes)
cis_elder_plot
```

## CSS

```{r}
css_children_plot = create_bubble_plot(css_children, title = 'a', shared_axes = css_axes)
css_children_plot
```

```{r}
css_adult_plot = create_bubble_plot(css_adult, title = 'b', shared_axes = css_axes)
css_adult_plot
```

```{r}
css_elder_plot = create_bubble_plot(css_elder, title = 'c', shared_axes = css_axes)
css_elder_plot
```


# Arranging

## All main results

```{r}
blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
  cowplot::theme_nothing()

legend = get_legend(
  p2_children_plot + 
    theme(legend.position = "right") + 
    theme(legend.position = c(0.5, 0.5)))

arranged = ggarrange(
  p2_children_plot + theme(legend.position = "none"),
  p2_adult_plot + theme(legend.position = "none"),
  p2_elder_plot + theme(legend.position = "none"),
  legend,
  ncol = 2,
  nrow = 2) + 
  colour_scale_all +
  guides(colour = guide_legend(override.aes = list(size=10)))

ggsave('Figures/Alignment/p2_age_stratified_loose.png', arranged, height = 9, width = 9)
```


```{r}
blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
  cowplot::theme_nothing()

legend = get_legend(
  sgss_children_plot + 
    theme(legend.position = "right") + 
    theme(legend.position = c(0.5, 0.5)))

arranged = ggarrange(
  sgss_children_plot + theme(legend.position = "none"),
  sgss_adult_plot + theme(legend.position = "none"),
  sgss_elder_plot + theme(legend.position = "none"),
  legend,
  ncol = 2,
  nrow = 2) + 
  colour_scale_all +
  guides(colour = guide_legend(override.aes = list(size=10)))

ggsave('Figures/Alignment/sgss_age_stratified_loose.png', arranged, height = 9, width = 9)
```

```{r}
blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
  cowplot::theme_nothing()

legend = get_legend(
  sgss_children_plot + 
    theme(legend.position = "right") + 
    theme(legend.position = c(0.5, 0.5)))

arranged = ggarrange(
  cis_children_plot + theme(legend.position = "none"),
  cis_adult_plot + theme(legend.position = "none"),
  cis_elder_plot + theme(legend.position = "none"),
  legend,
  ncol = 2,
  nrow = 2) + 
  colour_scale_all +
  guides(colour = guide_legend(override.aes = list(size=10)))

ggsave('Figures/Alignment/cis_age_stratified_loose.png', arranged, height = 9, width = 9)
```

```{r}
blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
  cowplot::theme_nothing()

legend = get_legend(
  sgss_children_plot + 
    theme(legend.position = "right") + 
    theme(legend.position = c(0.5, 0.5)))

arranged = ggarrange(
  css_children_plot + theme(legend.position = "none"),
  css_adult_plot + theme(legend.position = "none"),
  css_elder_plot + theme(legend.position = "none"),
  legend,
  ncol = 2,
  nrow = 2) + 
  colour_scale_all +
  guides(colour = guide_legend(override.aes = list(size=10)))

ggsave('Figures/Alignment/css_age_stratified_loose.png', arranged, height = 9, width = 9)
```
