---
title: "LPCA Visualisation"
output: html_notebook
---

```{r}
source('Visualisation/my_functions.R')
```


# Libraries

```{r}
library(ggplot2)
library(ggrepel)
library(reshape)
library(dplyr)
library(cowplot)
library(RColorBrewer)
library(ggpubr)
```

# Load data

```{r}
# entire populations
CTAS_pillar2 <- read.csv("Data/TTI_Pillar2/LPCA/symptoms_dataOriginP2_symp_loadings_K_2_par.csv")
CTAS_sgss <- read.csv("Data/TTI_SGSS/LPCA/symptoms_dataOriginSGSS_symp_loadings_K_2_par.csv")
CSS <- read.csv("Data/CovidSymptomStudy/LPCA/LPCA_SymptomLoadings_k2.csv")
ONS <- read.csv('Data/CommunityInfectionSurvey/LPCA/LPCA_SymptomLoadings_k_2.csv')

# Zoe
Zoe_children <- read.csv("Data/CovidSymptomStudyAgeSeperated/LPCA/LPCA_SymptomLoadings_k2_kids.csv")
Zoe_adults <- read.csv("Data/CovidSymptomStudyAgeSeperated/LPCA/LPCA_SymptomLoadings_k2_adults.csv")
Zoe_elder <- read.csv("Data/CovidSymptomStudyAgeSeperated/LPCA/LPCA_SymptomLoadings_k2_elder.csv")

# ONS
ONS_children <- read.csv('Data/CommunityInfectionSurveyAgeStratified/LPCA/LPCA_SymptomLoadings_18_k_2.csv')
ONS_adults <- read.csv('Data/CommunityInfectionSurveyAgeStratified/LPCA/LPCA_SymptomLoadings_18_55_k_2.csv')
ONS_elder <- read.csv('Data/CommunityInfectionSurveyAgeStratified/LPCA/LPCA_SymptomLoadings_56_k_2.csv')

# Pillar 2
p2_children <- read.csv('Data/TTI_Pillar2_AgeStratified/LPCA/symptoms_dataOriginP2Below18_symp_loadings_K_2_par.csv')
p2_adults <- read.csv('Data/TTI_Pillar2_AgeStratified/LPCA/symptoms_dataOriginP218-54_symp_loadings_K_2_par.csv')
p2_elder <- read.csv('Data/TTI_Pillar2_AgeStratified/LPCA/symptoms_dataOriginP255Plus_symp_loadings_K_2_par.csv')

# SGSS
sgss_children <- read.csv('Data/TTI_SGSS_AgeStratified/LPCA/symptoms_dataOriginSGSSBelow18_symp_loadings_K_2_par.csv')
sgss_adults <- read.csv('Data/TTI_SGSS_AgeStratified/LPCA/symptoms_dataOriginSGSS18-54_symp_loadings_K_2_par.csv')
sgss_elder <- read.csv('Data/TTI_SGSS_AgeStratified/LPCA/symptoms_dataOriginSGSS55Plus_symp_loadings_K_2_par.csv')
```


# Aligning principal components
Multiplying a principal component by -1 does not change the interpretation. We align some of the principal components for consistency of results.

```{r}
ONS_children = ONS_children %>%
  mutate(V2 = V2 * -1)

p2_children = p2_children %>%
  mutate(V2 = V2 * -1)

sgss_adults = sgss_adults %>%
  mutate(V2 = V2 * -1)

sgss_elder = sgss_elder %>%
  mutate(V2 = V2 * -1)

sgss_children = sgss_children %>%
  mutate(V1 = V1 * -1)

CSS = CSS %>%
  mutate(V2 = V2 * -1)

Zoe_adults = Zoe_adults %>%
  mutate(V2 = V2 * -1)

Zoe_elder = Zoe_elder %>%
  mutate(V2 = V2 * -1)
```


```{r}
SymptomNameLookup = read.csv('Data/Lookups/SymptomNameCategoryLookup.csv')
categories = read.csv('Data/Lookups/CategoriesLookup.csv')
```

# Clean data

```{r}
# entire populations
colnames(CTAS_pillar2) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(CTAS_sgss) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(CSS) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(ONS) <- c('symptom_name_raw', 'PC1', 'PC2')

# zoe
colnames(Zoe_children) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(Zoe_adults) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(Zoe_elder) <- c('symptom_name_raw', 'PC1', 'PC2')

# SGSS
colnames(sgss_children) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(sgss_adults) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(sgss_elder) <- c('symptom_name_raw', 'PC1', 'PC2')

# Pillar 2
colnames(p2_children) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(p2_adults) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(p2_elder) <- c('symptom_name_raw', 'PC1', 'PC2')

# ONS
colnames(ONS_children) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(ONS_adults) <- c('symptom_name_raw', 'PC1', 'PC2')
colnames(ONS_elder) <- c('symptom_name_raw', 'PC1', 'PC2')

```

```{r}
# entire populations
ONS_long = melt(ONS) %>%
inner_join(
   SymptomNameLookup %>% filter(dataset == 'ONS'),
   by = c('symptom_name_raw'))


CTAS_pillar2_long = melt(CTAS_pillar2) %>%
  inner_join(
    SymptomNameLookup %>% filter(dataset == 'CTAS'),
    by = c('symptom_name_raw'))

CTAS_sgss_long = melt(CTAS_sgss) %>%
  inner_join(
    SymptomNameLookup %>% filter(dataset == 'CTAS'),
    by = c('symptom_name_raw')) 

CSS_long = melt(CSS) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'Zoe'),
    by = c('symptom_name_raw'))

# Zoe - age stratified
Zoe_long_children = melt(Zoe_children) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'Zoe'),
    by = c('symptom_name_raw'))

 Zoe_long_adults = melt(Zoe_adults) %>%
   left_join(
     SymptomNameLookup %>% filter(dataset == 'Zoe'),
     by = c('symptom_name_raw'))

 Zoe_long_elder = melt(Zoe_elder) %>%
   left_join(
     SymptomNameLookup %>% filter(dataset == 'Zoe'),
     by = c('symptom_name_raw'))

# Pillar 2 - age stratified
p2_children_long = melt(p2_children) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'CTAS'),
    by = c('symptom_name_raw'))

p2_adults_long = melt(p2_adults) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'CTAS'),
    by = c('symptom_name_raw'))

p2_elder_long = melt(p2_elder) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'CTAS'),
    by = c('symptom_name_raw'))

# SGSS - age stratified
sgss_children_long = melt(sgss_children) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'CTAS'),
    by = c('symptom_name_raw'))

sgss_adults_long = melt(sgss_adults) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'CTAS'),
    by = c('symptom_name_raw'))

sgss_elder_long = melt(sgss_elder) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'CTAS'),
    by = c('symptom_name_raw'))


# ONS - age stratified
ONS_children_long = melt(ONS_children) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'ONS'),
    by = c('symptom_name_raw'))

ONS_adults_long = melt(ONS_adults) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'ONS'),
    by = c('symptom_name_raw'))

ONS_elder_long = melt(ONS_elder) %>%
  left_join(
    SymptomNameLookup %>% filter(dataset == 'ONS'),
    by = c('symptom_name_raw'))
```

# I removed the joins to symptom infor here, might need to add back in

```{r}
CTAS_pillar2 = CTAS_pillar2 %>%
  inner_join(SymptomNameLookup %>% filter(dataset == 'CTAS'))

CTAS_sgss = CTAS_sgss %>%
  inner_join(SymptomNameLookup %>% filter(dataset == 'CTAS'))

CSS = CSS %>%
   left_join(SymptomNameLookup %>% filter(dataset == 'Zoe'))

ONS = ONS %>%
  inner_join(SymptomNameLookup %>% filter(dataset == 'ONS'))

# zoe age stratified 
Zoe_children = Zoe_children %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'Zoe'))

Zoe_adults = Zoe_adults %>%
   left_join(SymptomNameLookup %>% filter(dataset == 'Zoe'))

Zoe_elder = Zoe_elder %>%
   left_join(SymptomNameLookup %>% filter(dataset == 'Zoe'))

# pillar 2 age stratified 
p2_children = p2_children %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'CTAS'))

p2_adults = p2_adults %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'CTAS'))

p2_elder = p2_elder %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'CTAS'))

# sgss age stratified 
sgss_children = sgss_children %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'CTAS'))

sgss_adults = sgss_adults %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'CTAS'))

sgss_elder = sgss_elder %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'CTAS'))

# ONS age stratified 
ONS_children = ONS_children %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'ONS'))

ONS_adults = ONS_adults %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'ONS'))

ONS_elder = ONS_elder %>%
  left_join(SymptomNameLookup %>% filter(dataset == 'ONS'))
```

# Vertical barplots

We try a third type of barplot to represent the logistic PCA components. The heatmaps are quite difficult to interpret in several ways, and it is difficult to encode category information onto them without making them visually challenging to read.

Instead, several vertical barplots with the bar fill are possibly a better representation.

# Pillar 2 - All

```{r}
levels_p2 = unique(
  CTAS_pillar2_long$symptom_name_formatted[
    order(
      CTAS_pillar2_long$category,
      CTAS_pillar2_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  CTAS_pillar2_long$symptom_name_formatted,
  levels=levels_p2,
  ordered = TRUE)

CTAS_pillar2_long$symptom_name_formatted <- factor(
  CTAS_pillar2_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )
```


```{r}
p2_bar = CTAS_pillar2_long %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) +
  geom_col() +
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') +
  ylab('Symptom') +
  labs(
  title = 'Pillar 2',
  fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
p2_bar
```

# Pillar 2 - Children

```{r}
levels_p2_children = unique(
  p2_children_long$symptom_name_formatted[
    order(
      p2_children_long$category,
      p2_children_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  p2_children_long$symptom_name_formatted,
  levels=levels_p2_children,
  ordered = TRUE)

p2_children_long$symptom_name_formatted <- factor(
  p2_children_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )
```


```{r}
p2_children_bar = p2_children_long %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) +
  geom_col() +
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') +
  ylab('Symptom') +
  labs(
  title = 'a',
  fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
p2_children_bar
```

# Pillar 2 - Adults

```{r}
levels_p2_adults = unique(
  p2_adults_long$symptom_name_formatted[
    order(
      p2_adults_long$category,
      p2_adults_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  p2_adults_long$symptom_name_formatted,
  levels=levels_p2_adults,
  ordered = TRUE)

p2_adults_long$symptom_name_formatted <- factor(
  p2_adults_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )
```


```{r}
p2_adults_bar = p2_adults_long %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) +
  geom_col() +
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') +
  ylab('Symptom') +
  labs(
  title = 'b',
  fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
p2_adults_bar
```
# Pillar 2 - Elder

```{r}
levels_p2_elder = unique(
  p2_elder_long$symptom_name_formatted[
    order(
      p2_elder_long$category,
      p2_elder_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  p2_elder_long$symptom_name_formatted,
  levels=levels_p2_elder,
  ordered = TRUE)

p2_elder_long$symptom_name_formatted <- factor(
  p2_elder_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )
```


```{r}
p2_elder_bar = p2_elder_long %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) +
  geom_col() +
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') +
  ylab('Symptom') +
  labs(
  title = 'c',
  fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
p2_elder_bar
```

## SGSS - all

```{r}
levels_CTAS_sgss = unique(
  CTAS_sgss_long$symptom_name_formatted[
    order(
      CTAS_sgss_long$category,
      CTAS_sgss_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  CTAS_sgss_long$symptom_name_formatted,
  levels=levels_CTAS_sgss,
  ordered = TRUE)

CTAS_sgss_long$symptom_name_formatted <- factor(
  CTAS_sgss_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )
```


```{r}
CTAS_sgss_bar = CTAS_sgss_long %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) + 
  geom_col() + 
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') + 
  ylab('Symptom') +
  labs(
    title = 'SGSS',
    fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
CTAS_sgss_bar
```

## SGSS - children

```{r}
levels_sgss_children = unique(
  CTAS_sgss_long$symptom_name_formatted[
    order(
      CTAS_sgss_long$category,
      CTAS_sgss_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  sgss_children_long$symptom_name_formatted,
  levels=levels_sgss_children,
  ordered = TRUE)

sgss_children_long$symptom_name_formatted <- factor(
  sgss_children_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )
```


```{r}
sgss_children_bar = sgss_children_long %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) + 
  geom_col() + 
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') + 
  ylab('Symptom') +
  labs(
  title = 'a',
  fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
sgss_children_bar
```

## SGSS - adults

```{r}
levels_sgss_adults = unique(
  sgss_adults_long$symptom_name_formatted[
    order(
      sgss_adults_long$category,
      sgss_adults_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  sgss_adults_long$symptom_name_formatted,
  levels=levels_sgss_adults,
  ordered = TRUE)

sgss_adults_long$symptom_name_formatted <- factor(
  sgss_adults_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )
```


```{r}
sgss_adults_bar = sgss_adults_long %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) +
  geom_col() +
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') +
  ylab('Symptom') +
  labs(
    'SGSS',
    title = 'b',
    fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
sgss_adults_bar
```

## SGSS - elder

```{r}
levels_sgss_elder = unique(
  CTAS_sgss_long$symptom_name_formatted[
    order(
      sgss_elder_long$category,
      sgss_elder_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  sgss_elder_long$symptom_name_formatted,
  levels=levels_sgss_elder,
  ordered = TRUE)

sgss_elder_long$symptom_name_formatted <- factor(
  sgss_elder_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )
```


```{r}
sgss_elder_bar = sgss_elder_long %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) +
  geom_col() +
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') +
  ylab('Symptom') +
  labs(
    title = 'c',
    fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) +
  colour_fill_all
sgss_elder_bar
```

## CSS

```{r}
levels_CSS = unique(
  CSS_long$symptom_name_formatted[
    order(
      CSS_long$category,
      CSS_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  CSS_long$symptom_name_formatted,
  levels=levels_CSS,
  ordered = TRUE)

CSS_long$symptom_name_formatted <- factor(
  CSS_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )

```


```{r}
CSS_bar = CSS_long %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) +
  geom_col() +
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') +
  ylab('Symptom') +
  labs(
  title = 'CSS',
  fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
CSS_bar
```

## Zoe children

```{r}
levels_zoe_children = unique(
  Zoe_long_children$symptom_name_formatted[
    order(
      Zoe_long_children$category,
      Zoe_long_children$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  Zoe_long_children$symptom_name_formatted,
  levels=levels_zoe_children,
  ordered = TRUE)

Zoe_long_children$symptom_name_formatted <- factor(
  Zoe_long_children$symptom_name_formatted,
  levels=levels(reordered_factor)
  )

```


```{r}
Zoe_bar_children = Zoe_long_children %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) + 
  geom_col() + 
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') + 
  ylab('Symptom') +
  labs(
  title = 'a',
  fill = 'Category') + 
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
Zoe_bar_children
```

## Zoe adults

```{r}
levels_zoe_adults = unique(
  Zoe_long_adults$symptom_name_formatted[
    order(
      Zoe_long_adults$category,
      Zoe_long_adults$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor_adults <- factor(
  Zoe_long_adults$symptom_name_formatted,
  levels=levels_zoe_adults,
  ordered = TRUE)

Zoe_long_adults$symptom_name_formatted <- factor(
  Zoe_long_adults$symptom_name_formatted,
  levels=levels(reordered_factor_adults)
  )

```


```{r}
Zoe_bar_adults = Zoe_long_adults %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) +
  geom_col() +
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') +
  ylab('Symptom') +
  labs(
  title = 'b',
  fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) +
  colour_fill_all
Zoe_bar_adults
```

## Zoe elder

```{r}
levels_zoe_elder = unique(
  Zoe_long_elder$symptom_name_formatted[
    order(
      Zoe_long_elder$category,
      Zoe_long_elder$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor_elder <- factor(
  Zoe_long_elder$symptom_name_formatted,
  levels=levels_zoe_elder,
  ordered = TRUE)

Zoe_long_elder$symptom_name_formatted <- factor(
  Zoe_long_elder$symptom_name_formatted,
  levels=levels(reordered_factor_elder)
  )

```


```{r}
Zoe_bar_elder = Zoe_long_elder %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4', 'PC5')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) +
  geom_col() +
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') +
  ylab('Symptom') +
  labs(
  title = 'c',
  fill = 'Category') +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) +
  colour_fill_all
Zoe_bar_elder
```

## ONS

```{r}
levels_ons = unique(
  ONS_long$symptom_name_formatted[
    order(
      ONS_long$category,
      ONS_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  ONS_long$symptom_name_formatted,
  levels=levels_ons,
  ordered = TRUE)

ONS_long$symptom_name_formatted <- factor(
  ONS_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )

```

```{r}
ONS_bar = ONS_long %>%
  mutate(category = factor(category)) %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) + 
  geom_col() + 
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') + 
  ylab('Symptom') +
  labs(
    title = 'CIS',
    fill = 'Category'
    ) +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
ONS_bar
```

## ONS - children

```{r}
levels_ons_children = unique(
  ONS_children_long$symptom_name_formatted[
    order(
      ONS_children_long$category,
      ONS_children_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  ONS_long$symptom_name_formatted,
  levels=levels_ons,
  ordered = TRUE)

ONS_children_long$symptom_name_formatted <- factor(
  ONS_children_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )

```

```{r}
ONS_children_bar = ONS_children_long %>%
  mutate(category = factor(category)) %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) + 
  geom_col() + 
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') + 
  ylab('Symptom') +
  labs(
    title = 'Children and adolescents (<18)',
    fill = 'Category'
    ) +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
ONS_children_bar
```

## ONS - adults

```{r}
levels_ons_adults = unique(
  ONS_adults_long$symptom_name_formatted[
    order(
      ONS_adults_long$category,
      ONS_adults_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  ONS_adults_long$symptom_name_formatted,
  levels=levels_ons_adults,
  ordered = TRUE)

ONS_adults_long$symptom_name_formatted <- factor(
  ONS_adults_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )

```

```{r}
ONS_adults_bar = ONS_adults_long %>%
  mutate(category = factor(category)) %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) + 
  geom_col() + 
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') + 
  ylab('Symptom') +
  labs(
    title = 'Adults (18-55)',
    fill = 'Category'
    ) +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
ONS_adults_bar
```

## ONS - elder

```{r}
levels_ons_elder = unique(
  ONS_elder_long$symptom_name_formatted[
    order(
      ONS_elder_long$category,
      ONS_elder_long$symptom_name_formatted,
      decreasing=TRUE
      )
    ]
  )

reordered_factor <- factor(
  ONS_elder_long$symptom_name_formatted,
  levels=levels_ons_elder,
  ordered = TRUE)

ONS_elder_long$symptom_name_formatted <- factor(
  ONS_elder_long$symptom_name_formatted,
  levels=levels(reordered_factor)
  )

```

```{r}
ONS_elder_bar = ONS_elder_long %>%
  mutate(category = factor(category)) %>%
  filter(variable %in% c('PC1', 'PC2', 'PC3', 'PC4')) %>%
  group_by(category) %>%
  ggplot(aes(x=value, y=symptom_name_formatted, fill=category)) + 
  geom_col() + 
  facet_wrap(~variable, nrow=1) +
  theme_minimal() +
  xlab('Loadings') + 
  ylab('Symptom') +
  labs(
    title = 'Elder (>55)',
    fill = 'Category'
    ) +
  scale_x_continuous(breaks = c(-0.4, 0, 0.4)) + 
  colour_fill_all
ONS_elder_bar
```


# Experimental all in one plot

It looks better when you save it to png...

```{r}
arranged = ggarrange(
  p2_bar,
  CTAS_sgss_bar, 
  CSS_bar, 
  ONS_bar, 
  common.legend = TRUE, 
  legend = 'bottom',
  nrow = 1,
  ncol = 4) +
  colour_fill_all

ggsave('Figures/LPCA/arranged_entire_pops.png', width = 12, height = 5)
```

```{r}
arranged_zoe_age_stratified = ggarrange(
  Zoe_bar_children,
   Zoe_bar_adults,
   Zoe_bar_elder,
  common.legend = TRUE, 
  legend = 'bottom',
  nrow = 3,
  ncol = 1) +
  colour_fill_all

ggsave('Figures/LPCA/arranged_zoe_age_stratified.png', width = 6, height = 16)
```

```{r}
arranged_ons_age_stratified = ggarrange(
  ONS_children_bar,
  ONS_adults_bar,
  ONS_elder_bar,
  common.legend = TRUE, 
  legend = 'bottom',
  nrow = 1,
  ncol = 3) +
  colour_fill_all

ggsave('Figures/LPCA/arranged_ons_age_stratified.png', width = 16, height = 6)
```

```{r}
arranged_p2_age_stratified = ggarrange(
  p2_children_bar,
  p2_adults_bar,
  p2_elder_bar,
  common.legend = TRUE, 
  legend = 'bottom',
  nrow = 3,
  ncol = 1) +
  colour_fill_all

ggsave('Figures/LPCA/arranged_p2_age_stratified.png', width = 6, height = 16)
```


```{r}
arranged_sgss_age_stratified = ggarrange(
  sgss_children_bar,
  sgss_adults_bar,
  sgss_elder_bar,
  common.legend = TRUE, 
  legend = 'bottom',
  nrow = 3,
  ncol = 1) +
  colour_fill_all

ggsave('Figures/LPCA/arranged_sgss_age_stratified.png', width = 6, height = 16)
```


