---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r}
library(ggplot2)
library(dplyr)
library(ggpubr)
library(knitr)
```

# Selected numbers of components:

See further down for model selection visualisations.

```{r, echo = FALSE, results = 'asis'}
dataset = c('CIS', 'CSS', 'P2', 'SGSS')
all = c(2,1,1,2)
children = c(1,1,1,1)
adults = c(2,1,1,2)
elder = c(1,1,1,1)

kable(data.frame(dataset, all, children, adults, elder))
```


```{r}
plot_deviance <- function(deviance_data, k_hat) {
  p1 = deviance_data %>%
    ggplot(aes(x = X, y = prop_dev)) + 
    geom_line() + 
    geom_point() +
    xlab('k') + 
    ylab('Proportion Bernoulli deviance explained') + 
    geom_vline(
      xintercept = k_hat + 0.5,
      color = 'red',
      linetype = "longdash") + 
    scale_x_continuous(breaks = 0:10) +
    ggtitle('a')
  
  p2 = deviance_data %>%
    ggplot(aes(x = X, y = marg_dev)) + 
    geom_line() + 
    geom_point() +
    xlab('k') + 
    ylab('Marginal Bernoulli deviance') + 
    geom_vline(
      xintercept = k_hat + 0.5,
      color = 'red',
      linetype = "longdash") + 
    scale_x_continuous(breaks = 0:10) +
    ggtitle('b')
  
  return(ggarrange(p1, p2))
}
```


# Community Infection Survey

```{r}
CIS = read.csv('Data/CommunityInfectionSurvey/LPCA/LPCA_deviance.csv')

# age stratified
CIS_18 = read.csv('Data/CommunityInfectionSurveyAgeStratified/LPCA/LPCA_deviance_18.csv')
CIS_18_54 = read.csv('Data/CommunityInfectionSurveyAgeStratified/LPCA/LPCA_deviance_18_54.csv')
CIS_55 = read.csv('Data/CommunityInfectionSurveyAgeStratified/LPCA/LPCA_deviance_55.csv')
```

## All

```{r}
number_components_selected = 2

plot_deviance(CIS, number_components_selected)
```

```{r}
out = plot_deviance(CIS, number_components_selected)
ggsave(filename = 'LPCA_ModelSelectionPlot.png', output, width = 7, height = 4)
```


## Children

```{r}
number_components_selected = 1

plot_deviance(CIS_18, number_components_selected)
```

## Adults

```{r}
number_components_selected = 2

plot_deviance(CIS_18_54, number_components_selected)
```

## Elders

```{r}
number_components_selected = 1

plot_deviance(CIS_55, number_components_selected)
```

# Covid Symptom Study

```{r}
CSS = read.csv('Data/CovidSymptomStudy/LPCA/LPCADevianceWide.csv')

CSS_18 = read.csv('Data/CovidSymptomStudyAgeSeperated/LPCA/LPCADevianceChildren.csv')
CSS_18_54 = read.csv('Data/CovidSymptomStudyAgeSeperated/LPCA/LPCADevianceAdults.csv')
CSS_55 = read.csv('Data/CovidSymptomStudyAgeSeperated/LPCA/LPCADevianceElder.csv')
```

## All

```{r}
number_components_selected = 1

plot_deviance(CSS, number_components_selected)
```

## Children

```{r}
number_components_selected = 1

plot_deviance(CSS_18, number_components_selected)
```

## Adults

```{r}
number_components_selected = 1

plot_deviance(CSS_18_54, number_components_selected)
```

## Elders

```{r}
number_components_selected = 1

plot_deviance(CIS_55, number_components_selected)
```

# Pillar 2 

```{r}
p2 = read.csv('Data/TTI_Pillar2/LPCA/LPCA_deviance_Origin_P2.csv')

p2_18 = read.csv('Data/TTI_Pillar2_AgeStratified/LPCA/LPCA_deviance_Origin_P2_Below_18.csv')
p2_18_54 = read.csv('Data/TTI_Pillar2_AgeStratified/LPCA/LPCA_deviance_Origin_P2_Between_18_and_54.csv')
p2_55 = read.csv('Data/TTI_Pillar2_AgeStratified/LPCA/LPCA_deviance_Origin_P2_55_Plus.csv')
```

## All

```{r}
number_components_selected = 1

plot_deviance(p2, number_components_selected)
```

## Children

```{r}
number_components_selected = 1

plot_deviance(p2_18, number_components_selected)
```

## Adults

```{r}
number_components_selected = 1

plot_deviance(p2_18_54, number_components_selected)
```

## Elders

```{r}
number_components_selected = 1

plot_deviance(p2_55, number_components_selected)
```

# SGSS


```{r}
sgss = read.csv('Data/TTI_SGSS/LPCA/LPCA_deviance_Origin_SGSS.csv')

sgss_18 = read.csv('Data/TTI_SGSS_AgeStratified/LPCA/LPCA_deviance_Origin_SGSS_Below_18.csv')
sgss_18_54 = read.csv('Data/TTI_SGSS_AgeStratified/LPCA/LPCA_deviance_Origin_SGSS_Between_18_54.csv')
sgss_55 = read.csv('Data/TTI_SGSS_AgeStratified/LPCA/LPCA_deviance_Origin_SGSS_55_Plus.csv')
```

## All

```{r}
number_components_selected = 2

plot_deviance(sgss, number_components_selected)
```

## Children

```{r}
number_components_selected = 1

plot_deviance(sgss_18, number_components_selected)
```

## Adults

```{r}
number_components_selected = 2

plot_deviance(sgss_18_54, number_components_selected)
```

## Elders

```{r}
number_components_selected = 1

plot_deviance(sgss_55, number_components_selected)
```


# Cross dataset comparisons

```{r}
compare_dev_cross_dataset = function(dev_data){
  p1 = ggplot(dev_data, aes(x=X, y=prop_dev, group=dataset, col=dataset, fill=dataset)) +
    geom_point(alpha = 0.7) +
    geom_line(size=1,alpha = 0.7) + 
    xlab('k') + 
    ylab('Proportion of deviance explained') + 
    scale_x_continuous(breaks = 0:10)

  p2 = ggplot(dev_data, aes(x=X, y=marg_dev, group=dataset, col=dataset, fill=dataset)) +
    geom_point(alpha = 0.7) +
    geom_line(size=1,alpha = 0.7) + 
    xlab('k') + 
    ylab('Proportion of deviance explained') + 
    scale_x_continuous(breaks = 0:10)
  
  return(ggarrange(p1, p2, common.legend = TRUE))
}
```


# Inter dataset comparisons

## CIS

```{r}
CIS$dataset = 'All'
CIS_18$dataset = 'Children'
CIS_18_54$dataset = 'Adults'
CIS_55$dataset = 'Elders'

all_CIS = rbind(CIS, CIS_18, CIS_18_54, CIS_55)
```

```{r}
out = compare_dev_cross_dataset(all_CIS)
```

```{r}
out
```


Would suggest 2 components, but children look like 1.

## CSS

```{r}
CSS$dataset = 'All'
CSS_18$dataset = 'Children'
CSS_18_54$dataset = 'Adults'
CSS_55$dataset = 'Elders'

all_CSS = rbind(CSS, CSS_18, CSS_18_54, CSS_55)
```

```{r}
out = compare_dev_cross_dataset(all_CSS)
```

```{r}
out
```


Would suggest just one component.

# Pillar 2

```{r}
p2$dataset = 'All'
p2_18$dataset = 'Children'
p2_18_54$dataset = 'Adults'
p2_55$dataset = 'Elders'

all_p2 = rbind(p2, p2_18, p2_18_54, p2_55)
```

```{r}
out = compare_dev_cross_dataset(all_p2)
```

```{r}
out
```


Looks like just one component to me.

# SGSS

```{r}
sgss$dataset = 'All'
sgss_18$dataset = 'Children'
sgss_18_54$dataset = 'Adults'
sgss_55$dataset = 'Elders'

all_sgss = rbind(sgss, sgss_18, sgss_18_54, sgss_55)
```

```{r}
out = compare_dev_cross_dataset(all_sgss)
```

```{r}
out
```

2 components: adults, all
1 component: children, elders

## All

```{r}
CIS$dataset = 'CIS'
CSS$dataset = 'CSS'
p2$dataset = 'Pillar 2'
sgss$dataset = 'SGSS'

all = rbind(CIS, CSS, p2, sgss)
```

```{r}
out = compare_dev_cross_dataset(all)
```

```{r}
out
```


CIS looks like 2, others look like 1

## Children

```{r}
CIS_18$dataset = 'CIS'
CSS_18$dataset = 'CSS'
p2_18$dataset = 'Pillar 2'
sgss_18$dataset = 'SGSS'

all_18 = rbind(CIS_18, CSS_18, p2_18, sgss_18)
```

```{r}
out = compare_dev_cross_dataset(all_18)
```

```{r}
out
```

All look like 1 component to me

## Adults

```{r}
CIS_18_54$dataset = 'CIS'
CSS_18_54$dataset = 'CSS'
p2_18_54$dataset = 'Pillar 2'
sgss_18_54$dataset = 'SGSS'

all_18_54 = rbind(CIS_18_54, CSS_18_54, p2_18_54, sgss_18_54)
```

```{r}
out = compare_dev_cross_dataset(all_18_54)
```

```{r}
out
```

CIS has 2, others have 1

## Elders

```{r}
CIS_55$dataset = 'CIS'
CSS_55$dataset = 'CSS'
p2_55$dataset = 'Pillar 2'
sgss_55$dataset = 'SGSS'

all_55 = rbind(CIS_55, CSS_55, p2_55, sgss_55)
```

```{r}
out = compare_dev_cross_dataset(all_55)
```

```{r}
out
```
