---
title: "SymptomFrequencies"
author: "Martyn Fyles"
date: "04/12/2020"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
library(cowplot)
library(reshape)
library(scico)
library(RColorBrewer)
```

# Data loading

Read in symptom info tables

```{r}
# entire populations
CTAS_pillar2_info = read.csv('Data/TTI_Pillar2/Symptom_infoOriginP2.csv')
CTAS_sgss_info = read.csv('Data/TTI_SGSS/Symptom_infoOriginSGSS.csv')
ONS_info = read.csv('Data/CommunityInfectionSurvey/symptoms_info.csv')
Zoe_info = read.csv('Data/CovidSymptomStudy/DemographicSymptom_wide.csv')
```

Read in the lookup tables

```{r}
SymptomNameCategoryLookup = read.csv(
  'Data/Lookups/SymptomNameCategoryLookup.csv'
  )
```

# Data cleaning

```{r}
colnames(CTAS_pillar2_info)[1] <- 'symptom_name_raw'
colnames(CTAS_sgss_info)[1] <- 'symptom_name_raw'
colnames(ONS_info)[2] <- 'symptom_name_raw'
colnames(Zoe_info)[2] <- 'symptom_name_raw'
```


# Data wrangling

Join the tables to the lookup, filtering down to their respective entries. Rename the symptom proportion column to a standardized name, and mutate variables to standardized units where possible.

```{r}
CTAS_pillar2_symp_props = CTAS_pillar2_info %>%
  inner_join(
    SymptomNameCategoryLookup) %>%
  filter(
    dataset == 'CTAS') %>%
  mutate(
    prop_with_symptom = proportion_of_cases_with_symptom) %>%
  select(
    dataset,
    symptom_name_formatted,
    prop_with_symptom,
    category
    )

CTAS_sgss_symp_props = CTAS_sgss_info %>%
  inner_join(
    SymptomNameCategoryLookup) %>%
  filter(
    dataset == 'CTAS') %>%
  mutate(
    prop_with_symptom = proportion_of_cases_with_symptom) %>%
  select(
    dataset,
    symptom_name_formatted,
    prop_with_symptom,
    category
    )

ONS_symp_props = ONS_info %>%
  inner_join(
    SymptomNameCategoryLookup) %>%
  filter(
    dataset == 'ONS') %>%
  mutate(
    prop_with_symptom = proportion_fromsymptomatics/100) %>%
  select(
    dataset,
    symptom_name_formatted,
    prop_with_symptom,
    category
    )

Zoe_symp_props = Zoe_info %>%
  inner_join(SymptomNameCategoryLookup) %>%
  filter(dataset == 'Zoe') %>%
  mutate(
    prop_with_symptom = proportion) %>%
  select(
    dataset,
    symptom_name_formatted,
    prop_with_symptom,
    category
    )
```
## Adding a name column to the datasets

```{r}
CTAS_pillar2_symp_props$name = "NHS Test & Trace\nPillar 2"
CTAS_sgss_symp_props$name = "NHS Test & Trace\nSGSS"
ONS_symp_props$name = "ONS Community\nInfection Survey"
Zoe_symp_props$name = "Covid Symptom Study"
```


Append all symptom proportion data together.

```{r}
all_symptom_proportions = bind_rows(
  CTAS_pillar2_symp_props,
  CTAS_sgss_symp_props,
  ONS_symp_props,
  Zoe_symp_props
  )
```

```{r}
all_symptom_proportions %>% distinct(symptom_name_formatted) %>% arrange(symptom_name_formatted)
```


# Symptom frequency plots

```{r}
    # geom_col(
    #   width = .9,
    #   orientation = 'prop_with_symptom',
    #   position = position_dodge2(
    #     preserve = "single",
    #     width = 10)) +
```

```{r}
#expand.grid(, KEEP.OUT.ATTRS = TRUE, stringsAsFactors = TRUE)
```

This is a really horrible hack to make the plots nice. Essentially, we want to have explicit NA's for symptom that are not collected by a dataset. This means the plotting will leave an empty space, which makes my life easier when arranging the plots later on.

```{r}
symptoms = all_symptom_proportions %>% distinct(symptom_name_formatted)
datasets = all_symptom_proportions %>% distinct(name)
all_combinations = expand.grid.df(symptom_name_fromatted = symptoms, name = datasets)

symptom_with_category = all_combinations %>%
  left_join(SymptomNameCategoryLookup, by = 'symptom_name_formatted') %>%
  distinct(category, symptom_name_formatted)

all_combinations = all_combinations %>% left_join(symptom_with_category)

# join to the original dataset, then work out which combinations do not 
# exist in the data
missing_symptom_dataset_combos = all_combinations %>%
  left_join(all_symptom_proportions) %>%
  filter(is.na(prop_with_symptom)) %>%
  mutate(prop_with_symptom = NA) %>%
  select(
    symptom_name_formatted,
    prop_with_symptom,
    category,
    name) %>%
  left_join(
    all_symptom_proportions %>% distinct(dataset, name)
  )
```

```{r}
colnames(all_symptom_proportions)
```

```{r}
missing_symptom_dataset_combos %>%
  distinct(dataset, symptom_name_formatted) %>%
  arrange(dataset, symptom_name_formatted)
```


```{r}
all_possible_symptom_proportions = rbind(all_symptom_proportions, missing_symptom_dataset_combos)
```

# Confidence interval

```{r}
name <- c('NHS Test & Trace\nPillar 2','NHS Test & Trace\nSGSS', 'ONS Community\nInfection Survey', 'Covid Symptom Study')
sample_size = c(1637965, 112925, 9165, 6163)

sample_size_df = data.frame(name, sample_size)

all_possible_symptom_proportions = all_possible_symptom_proportions %>%
  left_join(sample_size_df) %>%
  mutate(lower_ci = qbeta(0.025, shape1 = prop_with_symptom*sample_size + 0.5, shape2 = sample_size - prop_with_symptom*sample_size + 0.5)) %>%
  mutate(upper_ci = qbeta(1-0.025, shape1 = prop_with_symptom*sample_size + 0.5, shape2 = sample_size - prop_with_symptom*sample_size + 0.5))
```

```{r}
all_possible_symptom_proportions %>% distinct()
```


```{r}
category_names <- c(
  'a' = 'Altered state',
  'b' = 'Gastrointestinal',
  'c' = 'Lower respiratory tract',
  'd' = 'Other',
  'e' = 'Systemic',
  'f' = 'Upper respiratory tract'
)
```


```{r}
id = c('a', 'b', 'c', 'd', 'e', 'f')
category = c(
  'Altered state',
  'Gastrointestinal',
  'Lower respiratory tract',
  'Other',
  'Systemic',
  'Upper respiratory tract')
category_lookup = data.frame(category, id)
```


```{r}
make_horizontal_plot_nature = function(data_in, title){
  return(
    ggplot(
      data = data_in,
      aes(
        x = symptom_name_formatted,
        y = prop_with_symptom * 100,
        group = name,
        fill = name)) +
    geom_bar(
      stat = 'identity',
      position = 'dodge2') +
    scale_fill_brewer(
    type = "qual",
    palette = 2,
    direction = 1,
    aesthetics = "fill") +
    geom_errorbar(
      aes(
        ymin = lower_ci * 100,
        ymax = upper_ci * 100,
        fill = name),
      position = position_dodge2(
        width = 0.5,
        padding = 0.5)) + 
    ylim(0, 100) + 
    facet_wrap(
      ~ id,
      ncol = 3,
      scales = 'free_x') +
    theme_minimal_grid() +
    theme(
      legend.position = 'bottom',
      panel.spacing = unit(3, 'lines'),
      strip.text = element_text(hjust = 0, size = 16),
      axis.text.x = element_text(
        angle = 45,
        hjust = 1)) +
    xlab('Symptom') +
    ylab('Symptom frequency (%)') +
    labs(fill = 'Dataset') +
    scale_x_discrete(drop = FALSE)
  )
}

  

horiz_all = make_horizontal_plot_nature(
  all_possible_symptom_proportions %>% distinct() %>% left_join(category_lookup), title = 'Proportion of symptomatic case with symptom')
horiz_all
ggsave('Figures/DescriptiveStatistics/SymptomFrequenciesHorizontal.png', width = 15, height = 12)
```


```{r}
make_horizontal_plot = function(data_in, title){
  return(
    ggplot(
      data = data_in,
      aes(
        x = symptom_name_formatted,
        y = prop_with_symptom * 100,
        group = name,
        fill = name)) +
    geom_bar(
      stat = 'identity',
      position = 'dodge2') +
    scale_fill_brewer(
    type = "qual",
    palette = 2,
    direction = 1,
    aesthetics = "fill") +
    geom_errorbar(
      aes(
        ymin = lower_ci * 100,
        ymax = upper_ci * 100,
        fill = name),
      position = position_dodge2(
        width = 0.5,
        padding = 0.5)) + 
    ylim(0, 100) + 
    facet_wrap(
      ~ category,
      ncol = 3,
      scales = 'free_x') +
    theme_minimal_grid() +
    theme(
      legend.position = 'bottom',
      panel.spacing = unit(3, 'lines'),
      strip.text = element_text(hjust = 0, size = 16),
      axis.text.x = element_text(
        angle = 45,
        hjust = 1)) +
    xlab('Symptom') +
    ylab('Symptom frequency (%)') +
    labs(fill = 'Dataset') +
    scale_x_discrete(drop = FALSE)
  )
}

  

horiz_all = make_horizontal_plot(
  all_possible_symptom_proportions, title = 'Proportion of symptomatic case with symptom')
horiz_all
ggsave('Figures/DescriptiveStatistics/SymptomFrequenciesHorizontal.png', width = 15, height = 12)
```

```{r}
write.csv(file = 'Data/SymptomFrequencies.csv', all_symptom_proportions)
```


