---
title: "UMAP Visualisation"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r}
source('Visualisation/my_functions.R')
```

# Libraries

```{r}
library(ggplot2)
library(ggrepel)
library(dplyr)
library(cowplot)
library(RColorBrewer)
library(gridExtra)
library(ggpubr)
```

# Load and clean data

## Pillar 2 - all

```{r}
p2 <- read.csv("Data/TTI_Pillar2/SymptomsUMAP_loose_clusteringOrigin P2.csv")
# transpose and drop the index column
p2 = data.frame(t(p2[-1]))
p2$Symptom = rownames(p2)
p2 = p2 %>%
  select(Symptom,
         X1,
         X2)

# theta = -pi/4
# p2 = p2 %>%
#   mutate(
#     X1_dash = X1*cos(theta) - X2*sin(theta),
#     X2_dash = X1*sin(theta) + X2*cos(theta)) %>%
#   mutate(
#     X1 = X1_dash, 
#     X2 = X2_dash) %>%
#   select(
#     Symptom,
#     X1,
#     X2)
```

## Pillar 2 - children

```{r}
p2_children <- read.csv("Data/TTI_Pillar2_AgeStratified/SymptomsUMAP_loose_clusteringOriginP2below18.csv")
# transpose and drop the index column
p2_children = data.frame(t(p2_children[-1]))
p2_children$Symptom = rownames(p2_children)
p2_children = p2_children %>%
  select(Symptom,
         X1,
         X2)
```

## Pillar 2 - adults

```{r}
p2_adults <- read.csv("Data/TTI_Pillar2_AgeStratified/SymptomsUMAP_loose_clusteringOriginP218-54.csv")
# transpose and drop the index column
p2_adults = data.frame(t(p2_adults[-1]))
p2_adults$Symptom = rownames(p2_adults)
p2_adults = p2_adults %>%
  select(Symptom,
         X1,
         X2)
```

## Pillar 2 - elders

```{r}
p2_elder <- read.csv("Data/TTI_Pillar2_AgeStratified/SymptomsUMAP_loose_clusteringOriginP255Plus.csv")
# transpose and drop the index column
p2_elder = data.frame(t(p2_elder[-1]))
p2_elder$Symptom = rownames(p2_elder)
p2_elder = p2_elder %>%
  select(Symptom,
         X1,
         X2)
```

## SGSS - all

```{r}
sgss <- read.csv("Data/TTI_SGSS/SymptomsUMAP_loose_clusteringOrigin SGSS.csv")
# transpose and drop the index column
sgss = data.frame(t(sgss[-1]))
sgss$Symptom = rownames(sgss)
sgss = sgss %>%
  select(Symptom,
         X1,
         X2)
```

## SGSS - children

```{r}
sgss_children <- read.csv("Data/TTI_SGSS_AgeStratified/SymptomsUMAP_loose_clusteringOriginSGSSBelow18.csv")
# transpose and drop the index column
sgss_children = data.frame(t(sgss_children[-1]))
sgss_children$Symptom = rownames(sgss_children)
sgss_children = sgss_children %>%
  select(Symptom,
         X1,
         X2)
```

## SGSS - adults

```{r}
sgss_adults <- read.csv("Data/TTI_SGSS_AgeStratified/SymptomsUMAP_loose_clusteringOriginSGSS18-54.csv")
# transpose and drop the index column
sgss_adults = data.frame(t(sgss_adults[-1]))
sgss_adults$Symptom = rownames(sgss_adults)
sgss_adults = sgss_adults %>%
  select(Symptom,
         X1,
         X2)
```

## SGSS - elders

```{r}
sgss_elders <- read.csv("Data/TTI_SGSS_AgeStratified/SymptomsUMAP_loose_clusteringOriginSGSS55Plus.csv")
# transpose and drop the index column
sgss_elders = data.frame(t(sgss_elders[-1]))
sgss_elders$Symptom = rownames(sgss_elders)
sgss_elders = sgss_elders %>%
  select(Symptom,
         X1,
         X2)
```

## Zoe all

```{r}
zoe = read.csv('Data/CovidSymptomStudy/UMAPLooseWide.csv')
zoe = data.frame(t(zoe[-1]))
zoe$Symptom = rownames(zoe)
zoe = zoe %>%
  select(
    Symptom,
    X1,
    X2
  )
```

## Zoe children

```{r}
zoe_children = read.csv('Data/CovidSymptomStudyAgeSeperated/UMAPLoose_children.csv')
zoe_children = data.frame(t(zoe_children[-1]))
zoe_children$Symptom = rownames(zoe_children)
zoe_children = zoe_children %>%
  select(
    Symptom,
    X1,
    X2
  )
```

## Zoe adults

```{r}
zoe_adults = read.csv('Data/CovidSymptomStudyAgeSeperated/UMAPLoose_adults.csv')
zoe_adults = data.frame(t(zoe_adults[-1]))
zoe_adults$Symptom = rownames(zoe_adults)
zoe_adults = zoe_adults %>%
  select(
    Symptom,
    X1,
    X2
  )
```

## Zoe elder

```{r}
zoe_elder = read.csv('Data/CovidSymptomStudyAgeSeperated/UMAPLoose_elder.csv')
zoe_elder = data.frame(t(zoe_elder[-1]))
zoe_elder$Symptom = rownames(zoe_elder)
zoe_elder = zoe_elder %>%
  select(
    Symptom,
    X1,
    X2
  )
```

## ONS

```{r}
ONS = read.csv('Data/CommunityInfectionSurvey/SymptomsUMAP_loose_clustering.csv')
ONS = data.frame(t(ONS))[-1,]
ONS$symptom_name_raw = rownames(ONS)
ONS = ONS %>%
  select(
    symptom_name_raw,
    X1,
    X2
  )
rownames(ONS) = NULL
```

## ONS children

```{r}
ONS_children = read.csv('Data/CommunityInfectionSurveyAgeStratified/SymptomsUMAP_loose_clustering_18.csv')
ONS_children = data.frame(t(ONS_children))[-1,]
ONS_children$symptom_name_raw = rownames(ONS_children)
ONS_children = ONS_children %>%
  select(
    symptom_name_raw,
    X1,
    X2
  )
rownames(ONS_children) = NULL
```

## ONS adults

```{r}
ONS_adults = read.csv('Data/CommunityInfectionSurveyAgeStratified/SymptomsUMAP_loose_clustering_18_54.csv')
ONS_adults = data.frame(t(ONS_adults))[-1,]
ONS_adults$symptom_name_raw = rownames(ONS_adults)
ONS_adults = ONS_adults %>%
  select(
    symptom_name_raw,
    X1,
    X2
  )
rownames(ONS_adults) = NULL
```

## ONS elders

```{r}
ONS_elders = read.csv('Data/CommunityInfectionSurveyAgeStratified/SymptomsUMAP_loose_clustering_55.csv')
ONS_elders = data.frame(t(ONS_elders))[-1,]
ONS_elders$symptom_name_raw = rownames(ONS_elders)
ONS_elders = ONS_elders %>%
  select(
    symptom_name_raw,
    X1,
    X2
  )
rownames(ONS_elders) = NULL
```

# Joining to symptom_info tables and symptom name formatting lookups

Import the SymptomNameCategoryLookup which maps symptom names to formatted version and establishes uniform naming conventions.
```{r}
SymptomNameCategoryLookup = read.csv('Data/Lookups/SymptomNameCategoryLookup.csv')
categories = read.csv('Data/Lookups/CategoriesLookup.csv')
```

## p2 - all

```{r}
p2_symptom_info = read.csv('Data/TTI_Pillar2/Symptom_infoOriginP2.csv')
# establish the naming convention
colnames(p2)[1] = 'symptom_name_raw'
colnames(p2_symptom_info)[1] = 'symptom_name_raw'
p2 = p2 %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(p2_symptom_info)
```

## p2 - children

```{r}
p2_children_symptom_info = read.csv('Data/TTI_Pillar2_AgeStratified/Symptom_infoOriginP2Below18.csv')
# establish the naming convention
colnames(p2_children)[1] = 'symptom_name_raw'
colnames(p2_children_symptom_info)[1] = 'symptom_name_raw'
p2_children = p2_children %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(p2_children_symptom_info)
```

## p2 - adults

```{r}
p2_adults_symptom_info = read.csv('Data/TTI_Pillar2_AgeStratified/Symptom_infoOriginP218-54.csv')
# establish the naming convention
colnames(p2_adults)[1] = 'symptom_name_raw'
colnames(p2_adults_symptom_info)[1] = 'symptom_name_raw'
p2_adults = p2_adults %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(p2_adults_symptom_info)
```

## p2 - elder

```{r}
p2_elder_symptom_info = read.csv('Data/TTI_Pillar2_AgeStratified/Symptom_infoOriginP255Plus.csv')
# establish the naming convention
colnames(p2_elder)[1] = 'symptom_name_raw'
colnames(p2_elder_symptom_info)[1] = 'symptom_name_raw'
p2_elder = p2_elder %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(p2_elder_symptom_info)
```

## sgss - all

```{r}
sgss_symptom_info = read.csv('Data/TTI_SGSS/Symptom_infoOriginSGSS.csv')
# establish the naming convention
colnames(sgss)[1] = 'symptom_name_raw'
colnames(sgss_symptom_info)[1] = 'symptom_name_raw'
sgss = sgss %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(sgss_symptom_info) 
```

## sgss - children

```{r}
sgss_children_symptom_info = read.csv('Data/TTI_SGSS_AgeStratified/Symptom_infoOriginSGSSBelow18.csv')
# establish the naming convention
colnames(sgss_children)[1] = 'symptom_name_raw'
colnames(sgss_children_symptom_info)[1] = 'symptom_name_raw'
sgss_children = sgss_children %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(sgss_children_symptom_info) 
```

## sgss - adults

```{r}
sgss_adults_symptom_info = read.csv('Data/TTI_SGSS_AgeStratified/Symptom_infoOriginSGSS18-54.csv')
# establish the naming convention
colnames(sgss_adults)[1] = 'symptom_name_raw'
colnames(sgss_adults_symptom_info)[1] = 'symptom_name_raw'
sgss_adults = sgss_adults %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(sgss_adults_symptom_info) 
```

## sgss - elder

```{r}
sgss_elders_symptom_info = read.csv('Data/TTI_SGSS_AgeStratified/Symptom_infoOriginSGSS55Plus.csv')
# establish the naming convention
colnames(sgss_elders)[1] = 'symptom_name_raw'
colnames(sgss_elders_symptom_info)[1] = 'symptom_name_raw'
sgss_elders = sgss_elders %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'CTAS')) %>%
  inner_join(sgss_elders_symptom_info) 
```

## Zoe - all

```{r}
zoe_symptom_info = read.csv('Data/CovidSymptomStudy/DemographicSymptom_wide.csv')
# establish the naming convention
colnames(zoe)[1] = 'symptom_name_raw'
colnames(zoe_symptom_info)[2] = 'symptom_name_raw'
zoe = zoe %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'Zoe')) %>%
  inner_join(zoe_symptom_info) 
```

## Zoe - children

```{r}
zoe_symptom_info_children = read.csv('Data/CovidSymptomStudyAgeSeperated/DemographicSymptom_children.csv')
# establish the naming convention
colnames(zoe_children)[1] = 'symptom_name_raw'
colnames(zoe_symptom_info_children)[2] = 'symptom_name_raw'
zoe_children = zoe_children %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'Zoe')) %>%
  inner_join(zoe_symptom_info_children) 
```

## Zoe - adults

```{r}
zoe_symptom_info_adults = read.csv('Data/CovidSymptomStudyAgeSeperated/DemographicSymptom_adults.csv')
# establish the naming convention
colnames(zoe_adults)[1] = 'symptom_name_raw'
colnames(zoe_symptom_info_adults)[2] = 'symptom_name_raw'
zoe_adults = zoe_adults %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'Zoe')) %>%
  inner_join(zoe_symptom_info_adults)
```

## Zoe - elder

```{r}
zoe_symptom_info_elder = read.csv('Data/CovidSymptomStudyAgeSeperated/DemographicSymptom_elder.csv')
# establish the naming convention
colnames(zoe_elder)[1] = 'symptom_name_raw'
colnames(zoe_symptom_info_elder)[2] = 'symptom_name_raw'
zoe_elder = zoe_elder %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'Zoe')) %>%
  inner_join(zoe_symptom_info_elder) 
```

## ONS

```{r}
ONS_symptom_info = read.csv('Data/CommunityInfectionSurvey/symptoms_info.csv')
colnames(ONS_symptom_info)[2] = 'symptom_name_raw'
ONS = ONS %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'ONS')) %>%
  inner_join(ONS_symptom_info)
```

## ONS children

```{r}
ONS_children_symptom_info = read.csv('Data/CommunityInfectionSurveyAgeStratified/symptoms_info_18.csv')
colnames(ONS_children_symptom_info)[2] = 'symptom_name_raw'
ONS_children = ONS_children %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'ONS')) %>%
  inner_join(ONS_children_symptom_info)
```

## ONS adults

```{r}
ONS_adults_symptom_info = read.csv('Data/CommunityInfectionSurveyAgeStratified/symptoms_info_18_54.csv')
colnames(ONS_adults_symptom_info)[2] = 'symptom_name_raw'
ONS_adults = ONS_adults %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'ONS')) %>%
  inner_join(ONS_adults_symptom_info)
```

## ONS elder

```{r}
ONS_elder_symptom_info = read.csv('Data/CommunityInfectionSurveyAgeStratified/symptoms_info_55.csv')
colnames(ONS_elder_symptom_info)[2] = 'symptom_name_raw'
ONS_elders = ONS_elders %>%
  inner_join(SymptomNameCategoryLookup %>% filter(dataset == 'ONS')) %>%
  inner_join(ONS_elder_symptom_info)
```

Creating a ggplot object with setting that can be altered globally

```{r}
scaling_factor = 100
bubble_plot = geom_point(aes(size = scaling_factor * proportion_of_cases_with_symptom))
bubble_plot_zoe = geom_point(aes(size = scaling_factor * proportion))
```


```{r}
symptom_labels = labs(
    size = 'Proportion of cases\nwith symptom (%)',
    color = 'Symptom category'
    )
```

```{r}
category_legend = guides(colour = guide_legend(override.aes = list(size=5)))
```


```{r}
size_scaling =  scale_size_continuous(
    breaks = c(0, 20, 40, 60, 80, 100),
    labels = c(0, 20, 40, 60, 80, 100),
    limits = c(0, 100),
    range = c(2,6)
   )
```


# Plot Data

## Pillar 2 - all

```{r}
p2_plot = ggplot(
  p2,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) +
  bubble_plot +
  labs(
    title = "a") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels +
  size_scaling + 
  colour_scale_all +
  coord_equal(ratio = 1, xlim = c(9.2 - 2, 9.2 + 2), ylim = c(5.7 - 2, 5.7 + 2)) +
  category_legend +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
  theme(legend.position="bottom")
p2_plot
```

## Pillar 2 - Children

```{r}
p2_children_plot = ggplot(
  p2_children,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot + 
  labs(
    title = "a") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all +
  size_scaling + 
  coord_equal(ratio = 1, xlim = c(10 - 2.5, 10 + 2.5), ylim = c(6.3 - 2.5, 6.5 + 2.5)) + 
  category_legend +
  theme(legend.position="bottom") +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
p2_children_plot
```

## Pillar 2 - Adults

```{r}
p2_adults_plot = ggplot(
  p2_adults,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot + 
  labs(
    title = "b") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all +
  coord_equal(ratio = 1, xlim = c(4 - 2, 4 + 2), ylim = c(-0.75 - 2, -0.75 + 2)) + 
  category_legend +
  size_scaling +
  theme(legend.position="bottom") + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
p2_adults_plot
```

## Pillar 2 - Elders

```{r}
p2_elder_plot = ggplot(
  p2_elder,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot + 
  labs(
    title = "c") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all +
  coord_equal(ratio = 1, xlim = c(11.2 - 2.2, 11.2 + 2.2), ylim = c(3.5 - 2.2, 3.5 + 2.2)) + 
  category_legend +
  size_scaling +
  theme(legend.position="bottom") + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
p2_elder_plot
```

## SGSS - All

```{r}
sgss_plot = ggplot(
  sgss,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot + 
  labs(
    title = "b") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all +
  coord_equal(ratio = 1, xlim = c(0.75 - 2.5, 0.75 + 2.5), ylim = c(4.2 - 2.5, 4.2 + 2.5)) + 
  category_legend + 
  size_scaling + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
sgss_plot
```

## SGSS - Children

```{r}
sgss_children_plot = ggplot(
  sgss_children,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot + 
  labs(
    title = "a") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all +
  coord_equal(ratio = 1, xlim = c(6.2 - 2.5, 6.2 + 2.5), ylim = c(7.2 - 2.5, 7.2 + 2.5)) + 
  category_legend + 
  size_scaling +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
sgss_children_plot
```

## SGSS - Adults

```{r}
sgss_adults_plot = ggplot(
  sgss_adults,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot + 
  labs(
    title = "b") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all +
  coord_equal(ratio = 1, xlim = c(-1.4 - 3, -1.4 + 3), ylim = c(2.2 - 3, 2.2 + 3)) + 
  category_legend + 
  size_scaling + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
sgss_adults_plot
```

## SGSS - Elders

```{r}
sgss_elders_plot = ggplot(
  sgss_elders,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot + 
  labs(
    title = "c") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all +
  coord_equal(ratio = 1, xlim = c(12.5 - 2.2, 12.5 + 2.2), ylim = c(8.5 - 2.2, 8.5 + 2.2)) + 
  category_legend + 
  size_scaling + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
sgss_elders_plot
```

## Zoe

```{r}
zoe_plot = ggplot(
  zoe,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot_zoe + 
  labs(title = "c") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all + 
  coord_equal(ratio = 1, xlim = c(6.7 - 2, 6.7 + 2), ylim = c(3 - 2, 3 + 2)) +
  category_legend + 
  size_scaling + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
zoe_plot
```

## Zoe - Children

```{r}
zoe_plot_children = ggplot(
  zoe_children,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot_zoe + 
  labs(title = "a") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5
    ) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all + 
  coord_equal(ratio = 1, xlim = c(10.3 - 2.5, 10.3 + 2.5), ylim = c(-10.5- 2.5, -10.5 + 2.5)) +
  category_legend + 
  size_scaling + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
zoe_plot_children
```

## Zoe - Adults

```{r}
zoe_plot_adults = ggplot(
  zoe_adults,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot_zoe + 
  labs(title = "b") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5
    ) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all + 
  coord_equal(ratio = 1, xlim = c(5.7 - 2, 5.7 + 2), ylim = c(9.5 - 2, 9.5 + 2)) +
  category_legend +
  size_scaling + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
zoe_plot_adults
```

## Zoe - Elders

```{r}
zoe_plot_elder = ggplot(
  zoe_elder,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) + 
  bubble_plot_zoe + 
  labs(title = "c") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels + 
  colour_scale_all + 
  coord_equal(ratio = 1, xlim = c(4.5 - 1.8, 4.5 + 1.8), ylim = c(5.9 - 1.8, 5.9 + 1.8)) +
  category_legend + 
  size_scaling + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
zoe_plot_elder
```

## ONS

```{r}
ONS_plot = ggplot(
  ONS,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) +
  geom_point(
    aes(size = proportion_fromsymptomatics)
    ) +
  labs(title = "d") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5
    ) +
  theme_cowplot() +
  labs(
    size = 'Symptom frequency',
    color = 'Symptom category') +
  coord_equal(ratio = 1, xlim = c(10 - 2.5, 10 + 2.5), ylim = c(0.5 - 2.5, 0.5 + 2.5)) +
  colour_scale_all +
  category_legend + 
  size_scaling +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
ONS_plot
```

## ONS - Children

```{r}
ONS_children_plot = ggplot(
  ONS_children,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) +
  geom_point(
    aes(size = proportion_fromsymptomatics)
    ) +
  labs(title = 'a') +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5
    ) +
  theme_cowplot() +
  labs(
    size = 'Symptom frequency',
    color = 'Symptom category') +
  coord_equal(ratio = 1, xlim = c(23 - 2.5, 23 + 2.5), ylim = c(1.8 - 2.5, 1.8 + 2.5)) +
  colour_scale_all + 
  category_legend +
  size_scaling +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
ONS_children_plot
```

## ONS - Adults

```{r}
ONS_adults_plot = ggplot(
  ONS_adults,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) +
  geom_point(
    aes(size = proportion_fromsymptomatics)
    ) +
  labs(title = 'b') +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5
    ) +
  theme_cowplot() +
  labs(
    size = 'Symptom frequency',
    color = 'Symptom category') +
  coord_equal(ratio = 1, xlim = c(3 - 10, 3 + 10), ylim = c(1 - 10, 1 + 10)) +
  colour_scale_all + 
  category_legend + 
  size_scaling +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
ONS_adults_plot
```

## ONS - Elders

```{r}
ONS_elders_plot = ggplot(
  ONS_elders,
  aes(
    x=X1,
    y=X2,
    label=symptom_name_formatted,
    color = category)) +
  geom_point(
    aes(size = proportion_fromsymptomatics)
    ) +
  labs(title = 'c') +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = symptom_name_formatted),
    size = 2.5,
    point.padding = 0.5
    ) +
  theme_cowplot() +
  labs(
    size = 'Symptom frequency',
    color = 'Symptom category') +
  coord_equal(ratio = 1, xlim = c(6 - 2, 6 + 2), ylim = c(1 - 2, 1 + 2)) +
  colour_scale_all +
  category_legend + 
  size_scaling +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title = element_blank()) +
  grids()
ONS_elders_plot
```

# Arranging

## All main results

```{r}
blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
  cowplot::theme_nothing()

legend = get_legend(
  p2_plot + 
    theme(legend.position = "right") + 
    theme(legend.position = c(0, 0)))

arranged = ggarrange(
  p2_plot + theme(legend.position = "none"),
  sgss_plot + theme(legend.position = "none"),
  legend,
  zoe_plot + theme(legend.position = "none"),
  ONS_plot + theme(legend.position = "none"),
  blankPlot,
  ncol = 3,
  nrow = 2) + 
  colour_scale_all +
  guides(colour = guide_legend(override.aes = list(size=10)))

ggsave('Figures/UMAP/arranged_loose.png', arranged, height = 9, width = 9)
```

## Pillar 2 - age stratified

```{r}
legend = get_legend(p2_adults_plot + theme(legend.position = c(0.3, 0.5)))

arranged_p2_age_stratified = ggarrange(
  p2_children_plot + theme(legend.position = "none"),
  p2_adults_plot + theme(legend.position = "none"),
  p2_elder_plot + theme(legend.position = "none"),
  legend,
  nrow = 2,
  ncol = 2) + 
  colour_scale_all +
  guides(colour = guide_legend(override.aes = list(size=10)))

ggsave('Figures/UMAP/arranged_loose_p2_age_stratified.png', arranged_p2_age_stratified, height = 8, width = 8)
```

## SGSS - age stratified

```{r}
legend = get_legend(sgss_adults_plot + theme(legend.position = c(0.3, 0.5)))

arranged_sgss_age_stratified = ggarrange(
  sgss_children_plot + theme(legend.position = "none"),
  sgss_adults_plot + theme(legend.position = "none"),
  sgss_elders_plot + theme(legend.position = "none"),
  legend,
  nrow = 2,
  ncol = 2) + 
  colour_scale_all +
  guides(colour = guide_legend(override.aes = list(size=10)))

ggsave('Figures/UMAP/arranged_loose_sgss_age_stratified.png', arranged_sgss_age_stratified, height = 8, width = 8)
```

## ONS - age stratified

```{r}
legend = get_legend(sgss_adults_plot + theme(legend.position = c(0.3, 0.5)))

arranged_ons_age_stratified = ggarrange(
  ONS_children_plot + theme(legend.position = "none"),
  ONS_adults_plot + theme(legend.position = "none"),
  ONS_elders_plot + theme(legend.position = "none"),
  legend,
  nrow = 2,
  ncol = 2) + 
  colour_scale_all +
  guides(colour = guide_legend(override.aes = list(size=10)))

ggsave('Figures/UMAP/arranged_loose_ons_age_stratified.png', arranged_ons_age_stratified, height = 8, width = 8)
```

## Zoe age stratified

```{r}
legend = get_legend(zoe_plot_adults + theme(legend.position = c(0.3, 0.5)))

arranged_zoe_age_stratified = ggarrange(
  zoe_plot_children + theme(legend.position = "none"),
  zoe_plot_adults + theme(legend.position = "none"),
  zoe_plot_elder + theme(legend.position = "none"),
  legend,
  nrow = 2,
  ncol = 2)

ggsave('Figures/UMAP/arranged_loose_zoe_age_stratified.png', arranged_zoe_age_stratified, height = 8, width = 8)
```

# Saving single dataset outputs

#```{r}
# pillar 2 - all
# ggsave(
#   filename = '../Figures/UMAP/CTAS_pillar2_loose.png',
#   plot = p2_plot
#   )
# 
# # pillar 2 - children
# ggsave(
#   filename = '../Figures/UMAP/p2_children_loose.png',
#   plot = p2_children_plot
#   )
# 
# # pillar 2 - adults
# ggsave(
#   filename = '../Figures/UMAP/p2_adults_loose.png',
#   plot = p2_adults_plot
#   )
# 
# # pillar 2 - elders
# ggsave(
#   filename = '../Figures/UMAP/p2_elders_loose.png',
#   plot = p2_elder_plot
#   )
# 
# # sgss - all
# ggsave(
#   filename = '../Figures/UMAP/sgss_loose.png',
#   plot = sgss_plot
#   )
# 
# # sgss - children
# ggsave(
#   filename = '../Figures/UMAP/sgss_children_loose.png',
#   plot = sgss_children_plot
#   )
# 
# # sgss - adults
# ggsave(
#   filename = '../Figures/UMAP/sgss_adults_loose.png',
#   plot = sgss_adults_plot
#   )
# 
# # sgss - elders
# ggsave(
#   filename = '../Figures/UMAP/sgss_elder_loose.png',
#   plot = sgss_elders_plot
#   )
# 
# # zoe - all
# ggsave(
#   filename = '../Figures/UMAP/Zoe_loose.png',
#   plot = zoe_plot
#   )
# 
# # zoe - children
# ggsave(
#   filename = '../Figures/UMAP/Zoe_children_loose.png',
#   plot = zoe_plot_children
#   )
# 
# # zoe - adults
# ggsave(
#   filename = '../Figures/UMAP/Zoe_adults_loose.png',
#   plot = zoe_plot_adults
#   )
# 
# # zoe - elder
# ggsave(
#   filename = '../Figures/UMAP/Zoe_elders_loose.png',
#   plot = zoe_plot_elder
#   )
# 
# # ons - all
# ggsave(
#   filename = '../Figures/UMAP/ONS_loose.png',
#   plot = ONS_plot
#   )
# 
# # ons - children
# ggsave(
#   filename = '../Figures/UMAP/ONS_children_loose.png',
#   plot = ONS_plot
#   )
# 
# # ons - adults
# ggsave(
#   filename = '../Figures/UMAP/ONS_adults_loose.png',
#   plot = ONS_adults_plot
#   )
# 
# # ons - elders
# ggsave(
#   filename = '../Figures/UMAP/ONS_adults_loose.png',
#   plot = ONS_elders_plot
#   )
#```


