---
title: "UMAP Visualisation"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r}
source('Example/Visualisation/my_functions.R')
```

# Libraries

```{r}
library(ggplot2)
library(ggrepel)
library(dplyr)
library(cowplot)
library(RColorBrewer)
library(gridExtra)
library(ggpubr)
#library(lemon)
```

# Load and clean data

## Pillar 2 - all

```{r}
umap <- read.csv("Example/Outputs/SymptomsUMAP_loose_clustering.csv")
# transpose and drop the index column
umap = data.frame(t(umap[-1]))
umap$Symptom = rownames(umap)
umap = umap %>%
  select(Symptom,
         X1,
         X2)
```

# Joining to symptom_info tables and symptom name formatting lookups

Import the SymptomNameCategoryLookup which maps symptom names to formatted version and establishes uniform naming conventions.
```{r}
categories = read.csv('Example/Inputs/symptom_categories.csv')
```

## p2 - all

Join the umap outputs to the category lookup table and the symptom proportions table.

```{r}
symptom_props = read.csv('Example/Outputs/symptom_proportions.csv')
# establish the naming convention
#colnames(p2)[1] = 'symptom_name_raw'
colnames(symptom_props) = c('Symptom', 'proportion')
umap = umap %>%
  inner_join(categories) %>%
  inner_join(symptom_props)
```

Creating a ggplot object with setting that can be altered globally

```{r}
scaling_factor = 100
bubble_plot = geom_point(aes(size = scaling_factor * proportion))
```


```{r}
symptom_labels = labs(
    size = 'Proportion of cases\nwith symptom (%)',
    color = 'Symptom category'
    )
```

```{r}
category_legend = guides(colour = guide_legend(override.aes = list(size=5)))
```


# Plot Data

## Pillar 2 - all

```{r}
umap_plot = ggplot(
  umap,
  aes(
    x=X1,
    y=X2,
    label=Symptom,
    color = Category)) +
  bubble_plot +
  labs(
    title = "Synthetic Dataset") +
  geom_text_repel(
    inherit.aes = FALSE,
    aes(x=X1, y=X2, label = Symptom),
    size = 2.5,
    point.padding = 0.5) +
  theme_cowplot() +
  symptom_labels +
  colour_scale_all +
  scale_size_continuous() +
  category_legend
umap_plot
```

```{r}
ggsave('Example/Figures/UMAP_loose.png')
```



